Sequential rank agreement methods for comparison of ranked lists

### 2015-06-16 latex/paper.Rnw
Data og tekst

\end{center}
 \caption{Left panels: Sequential rank agreement for 4 different analysis methods
   applied to the 3051 genes in the Golub data. The two plots on the
   right show the sequential rank agreement for the same data but
   where only the top-\Sexpr{topk} ranked items are available. The blue
   and red areas correspond to the independent and randomized
   reference hypothesis areas, respectively. The bottom plots are
   identical to the corresponding top plots but have been zoomed in on
   the first part of the $x$ axis.}
 \label{fig:example1}
\end{figure}

@@

@@

in
\eqref{formula:censored-agreement}

Unless we have additional prior knowledge about the distribution of the
unranked items then we can restrict attention of the sequential rank
agreement to
\begin{equation}
d \leq \max(k_1, \ldots, k_L),
\end{equation}
since we have no information about the ordering of the items after a
depth $d$ where all lists are censored.

@@

FIXME: If instead of running through all elements of $\tilde R_1(X_p)$
one would use the average rank in $\tilde R_1(X_p)$ we would end up with
a too small variance.

FIXME: For censored lists we expect a change point around the depth
where the lists are censored. This is an artefact stemming from the
fact that

>>>>

\end{center}
 \caption{Left panels: Sequential rank agreement for 4 different analysis methods
   applied to the 3051 genes in the Golub data. Right panels:
   Corresponding xssequential rank agreement for the same data but
   where only the top \Sexpr{topk} ranked items are available. The blue
   and red areas correspond to the independent and randomized
   reference hypothesis areas, respectively. The bottom plots are
   identical to the corresponding top plots but have been zoomed in on
   the first part of the $x$ axis.}
 \label{fig:example1}
\end{figure}

@@

The proposed approach for censored rankings is based on two
assumptions: 1) that the items of interest will be ..., and that 2)
that the censored rankings provide so little information that it is
reasonable to assume that the missing rankings

For censored data it is also imminent that ...

@@

For censored lists we expect a change point around the depth
where the lists are censored. This is an artefact stemming from the
fact that

Unless we have additional prior knowledge about the distribution of the
unranked items then we can restrict attention of the sequential rank
agreement to
\begin{equation}
d \leq \max(k_1, \ldots, k_L),
\end{equation}
since we have no real information about the ordering of the items after a
depth $d$ where all lists are censored.

@@
